Challenging Fuel Cycle Modeling Assumptions: Facility and Time Step Discretization Effects

### 2016-02-05 paper.tex
...-based hyphens

Traditionally, many fuel cycle simulators have used a system dynamics approach
\cite{forrester_industrial_1961} to modeling. These simulators model several
\emph{stocks} representing isotopes or isotope groups that have quantities that change
over time because of \emph{flows} between them.  The flows are determined by equations
that are a function of the state of the system (i.e., the system's stocks).  A
constructed system is then solved in discrete or continuous time depending on
the limitations of the software and constraints imposed by the model.  In
system dynamics based simulators, the number of stocks and potential flows between
them is generally a static property of the modeled system, making it somewhat
difficult to swap different reactor models in and out of the same scenario
without wiring them into the simulator manually.

System dynamics based fuel cycle simulators generally use a collection of
stocks to represent the state of groups of like-facilities commonly referred
to as "fleets".  As the simulation steps through time, the levels of stocks
(e.g., reactor fresh fuel inventory, repository waste inventories, etc.) are
adjusted according to the calculated flow values.  Fuel cycle simulators that model
facility fleets built on a system dynamics foundation include VISION
\cite{jacobson_verifiable_2010}, DANESS \cite{van_den_durpel_daness_2009},
DYMOND, and ORION \cite{gregg_orion_2012} among
others.  In fleet-based modeling:

>>>>

Traditionally, many fuel cycle simulators have used a system dynamics approach
\cite{forrester_industrial_1961} to modeling. These simulators model several
\emph{stocks} representing isotopes or isotope groups that have quantities that change
over time because of \emph{flows} between them.  The flows are determined by equations
that are a function of the state of the system (i.e., the system's stocks).  A
constructed system is then solved in discrete or continuous time depending on
the limitations of the software and constraints imposed by the model.  In
system dynamics-based simulators, the number of stocks and potential flows between
them is generally a static property of the modeled system, making it somewhat
difficult to swap different reactor models in and out of the same scenario
without wiring them into the simulator manually.

System dynamics-based fuel cycle simulators generally use a collection of
stocks to represent the state of groups of like-facilities commonly referred
to as "fleets".  As the simulation steps through time, the levels of stocks
(e.g., reactor fresh fuel inventory, repository waste inventories, etc.) are
adjusted according to the calculated flow values.  Fuel cycle simulators that model
facility fleets built on a system dynamics foundation include VISION
\cite{jacobson_verifiable_2010}, DANESS \cite{van_den_durpel_daness_2009},
DYMOND, and ORION \cite{gregg_orion_2012} among
others.  In fleet-based modeling:
